MATH/COMP 562 ASSIGNMENT 2

### 2023-06-30 assignment-2/article.tex
Fix LaTeX formatting

	Thus, we have constructed a training sample S for which the 0-1 loss function has a local minimum but not a global minimum. This satisfies all conditions of the problem.
\end{solution}

@@

	To evaluate smoothness, we look at the second derivative of the loss function with respect to $w$. The Hessian is given by
	\[\nabla^2 \ell(w, (x, y)) = \frac{\exp(y\langle w, x \rangle)}{(1+\exp(y\langle w, x \rangle))^2}xx^T\]

@@

	\begin{align*}
		| \ell(w, (x, y)) - \ell(w', (x, y)) | & = | \max\{0, 1 - y\langle w, x \rangle\} - \max\{0, 1 - y\langle w', x \rangle\} |                                               \\
		                                       & \leq | y\langle w, x \rangle - y\langle w', x \rangle | \quad \text{(since max function is Lipschitz with Lipschitz constant 1)} \\
		                                       & = | y\langle w - w', x \rangle |                                                                                                 \\
		                                       & \leq \| y(x) \|_2 \| w - w' \|_2 \quad \text{(by Cauchy-Schwarz inequality)}                                                     \\
		                                       & \leq R \| w - w' \|_2 \quad \text{(since } \| x \|_2 \leq R \text{)}
	\end{align*}

>>>>

	Thus, we have constructed a training sample S for which the 0\textendash{}1 loss function has a local minimum but not a global minimum. This satisfies all conditions of the problem.
\end{solution}

@@

	To evaluate smoothness, we look at the second derivative of the loss function with respect to $w$. The Hessian is given by
	\[\nabla^2 \ell(w, (x, y)) = \frac{\exp(y\langle w, x \rangle)}{(1+{\exp(y\langle w, x \rangle)})^2} x x^T \]

@@

	\begin{align*}
		| \ell(w, (x, y)) - \ell(w', (x, y)) | & = | \max\{0, 1 - y\langle w, x \rangle\} - \max\{0, 1 - y\langle w', x \rangle\} |                                               \\
		                                       & \leq | y\langle w, x \rangle - y\langle w', x \rangle | \quad \text{(since max function is Lipschitz with Lipschitz constant 1)} \\
		                                       & = | y\langle w - w', x \rangle |                                                                                                 \\
		                                       & \leq \| y(x) \|_2 \| w - w' \|_2 \quad \text{(by Cauchy-Schwarz inequality)}                                                     \\
		                                       & \leq R \| w - w' \|_2 \quad \text{(since $\| x \|_2 = R$)}
	\end{align*}
